\section{Data Module}
	The Data module handles the interactions with the users and the server. Users from different platforms connect to the Access Channel which interacts which interacts with the upstream Manager. The up-stream Manager is the gateway for user requests and responses from the down-stream Manager. The down-stream manager gives all up-stream requests to the server and sends all server responses to the up-stream Manager. The Design patterns which are integrated into the Data Module are: Singleton, chain of responsibility, template, iterator and interface. the Singleton design pattern ensures only one UpStreamManager, DownStreamManager and AccessChannel exist at any time. The chain of responsibility design pattern is used to pass requests up from the user platforms to the server and to pass stream objects from the server to the user platforms. The template design pattern is used to implement different handling methods for the requests of the different concrete plate forms used to connect to the access channel. The iterator design pattern is used for the server to iterate through users when concurrently sending multiple stream objects to different users. The interface design pattern is used to implement how the server acts as an interface for all subsystems.

\section{Events Module}
This module is responsible for the notification of events to the user automatically, this is done by constant signals being sent to the server and back to device, as well as analysis of patterns in users event searches as well as the ones they attend often, and suggesting events of a similar genre to the student thus maximising the user exoerience giving the device a form of artificial intelligence as it will be able to communicate to the student an event they may be inclined to attend aswell.
